The competing effects of the immune system and EMT on epithelial cancers

### 2019-04-19 Paper/Paper.tex
First Intro Para's Updates to makes Adam's fixes

\section*{Abstract}
Preceding and during cancer progression, the immune system is engaged in complex sets of interactions with epithelia that affect tumor incidence and prognosis. Inflammation also has significant effects on gastrointestinal and pancreatic tumors.
Moreover, epithelial cell plasticity can significantly alter disease trajectories (for better or worse) via epithelial-to-mesenchymal transition (EMT). Several of the same pathways that regulate EMT are involved in tumor-immune interactions.
Yet little is known about the mechanisms and consequences of these regulatory processes.
Here we introduce a multiscale agent-based model to describe the interplay between tumor-immune-EMT interactions and their impact on epithelial tissues.
Through {\em in silico} analysis of large patient cohorts, we found controllable regimes that increase cancer-free survival. Delaying tumorigenesis depended crucially on properties of the mesenchymal phenotype: its growth rate and its immune-evasiveness.
We performed analysis of pancreatic cancer data from The Cancer Genome Atlas to compare clinical measurements with model predictions. We found, in broad agreement with the model, that association with EMT worsened the survival probabilities of inflammation-associated cancer.
These results offer novel means to delay disease onset by controlling properties of EMT and demonstrate the importance of studying cancer-immune interactions in the light of EMT.
%The model presented provides a base for future studies into the intricate regulation of tumorigenesis.

>>>>

\section*{Abstract}
Preceding and during cancer progression, the immune system is engaged in complex sets of interactions with epithelia that affect tumor incidence and prognosis. Inflammation also has significant effects on gastrointestinal and pancreatic tumors.
Moreover, epithelial cell plasticity can significantly alter disease trajectories (for better or worse) via epithelial-to-mesenchymal transition (EMT). Several of the same pathways that regulate EMT are involved in tumor-immune interactions, yet little is known about the mechanisms and consequences of these regulatory processes.
Here we introduce a multiscale evolutionary model to describe the interplay between tumor-immune-EMT interactions and their impact on epithelial tissues.
Through {\em in silico} analysis of large patient cohorts, we found controllable regimes that maximize cancer-free survival. Delaying tumorigenesis depended crucially on properties of the mesenchymal phenotype: its growth rate and its immune-evasiveness.
We performed analysis of pancreatic cancer data from The Cancer Genome Atlas to compare clinical measurements with model predictions. We found, in broad agreement with the model, that association with EMT worsened the survival probabilities of inflammation-associated cancer.
These results offer novel means to delay disease onset by regulating properties of EMT, and demonstrate the importance of studying cancer-immune interactions in the light of EMT.
%The model presented provides a base for future studies into the intricate regulation of tumorigenesis.
